The \dealii{} Library, Version 9.0

### 2018-04-04 9.0/paper.tex
Add myself to the authors

\hypersetup{
  pdfauthor={
    Timo Heister,
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

% \author[1]{Daniel Arndt}
% \affil[1]{Interdisciplinary Center for Scientific Computing,
%     Heidelberg University, Im Neuenheimer Feld 205, 69120 Heidelberg, Germany.
%     {\texttt{daniel.arndt@iwr.uni-heidelberg.de}}}
% 
% \author[2]{Wolfgang Bangerth}
% \affil[2]{Department of Mathematics, Colorado State University, Fort
%   Collins, CO 80523-1874, USA.
%     {\texttt{bangerth@colostate.edu}}}
% 
% \author[3]{Denis Davydov}
% \affil[3]{Chair of Applied Mechanics, University of
%      Erlangen-Nuremberg, Egerlandstr.\ 5, 91058 Erlangen, Germany.
%     {\texttt{denis.davydov@fau.de}}}

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Timo Heister,
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[1]{Daniel Arndt}
\affil[1]{Interdisciplinary Center for Scientific Computing,
  Heidelberg University,
  Im Neuenheimer Feld 205,
  69120 Heidelberg, Germany.
  {\texttt{daniel.arndt@iwr.uni-heidelberg.de}}}

% \author[2]{Wolfgang Bangerth}
% \affil[2]{Department of Mathematics, Colorado State University, Fort
%   Collins, CO 80523-1874, USA.
%     {\texttt{bangerth@colostate.edu}}}
% 
% \author[3]{Denis Davydov}
% \affil[3]{Chair of Applied Mechanics, University of
%      Erlangen-Nuremberg, Egerlandstr.\ 5, 91058 Erlangen, Germany.
%     {\texttt{denis.davydov@fau.de}}}
